\Title

### 2020-01-21 manuscript/manuscript.tex
Change g vector to g_z

\begin{equation}
    \mathbf{g}(\mathbf{p}) = \mathbf{A} \mathbf{m},
\end{equation}

\noindent where $\mathbf{g}(\mathbf{p})$ is the vector containing the measured
field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
masses of the point sources and $\mathbf{A}$ a matrix whose
elements can be obtained as:

\begin{equation}
    a_{ij} = G \frac{1}{|\mathbf{p}_i - \mathbf{q}_j|^2},
\end{equation}

>>>>

\begin{equation}
    g_z(\mathbf{p}) = \mathbf{A} \mathbf{m},
    \label{eq:linear-problem-g}
\end{equation}

\noindent where $g_z(\mathbf{p})$ is the vector containing the measured
field on the points $\mathbf{p}$, $\mathbf{m}$ is the vector containing the
masses of the point sources and $\mathbf{A}$ a matrix whose
elements can be obtained as the vertical component of the gravitational
acceleration measured on $\mathbf{p}$ due to the point mass on $\mathbf{q}$:

\begin{equation}
    a_{ij} = G \frac{(z_i - z_j)}{|\mathbf{p}_i - \mathbf{q}_j|^3},
\end{equation}

\noindent where $z_i$ and $z_j$ are the vertical components of the
$\mathbf{p}_i$ and $\mathbf{q}_j$ points, respectively.
